---
title: "Introduction to Data Science - HW 4"
author: "First Name Last name - `flastname@floridapoly.edu`"
output: html_notebook
---



# Problem 1 

Load the `tidyverse` package

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```

In this problem you will work with vehicle fuel economy data from the US EPA (Environmental Protection Agency), ranging from 1985-2015. 

Read the data using the code below:

```{r, message=FALSE, warning=FALSE}
vehicles <- read_csv("https://raw.githubusercontent.com/reisanar/datasets/master/vehicles.csv")
```

   Variable  | Description
-------------|-----------------------------------------
`id`         | Unique EPA identifier
`make`       | Manufacturer
`model`      | Model name
`year`       | Model year
`class`      | EPA vehicle size class
`trans`      | Transmission
`drive`      | Drive train
`cyl`        | Number of cylinders
`displ`      | Engine displacement, in litres
`fuel`       | Fuel type
`hwy`        | Highway fuel economy, in mpg
`cty`        | City fuel economy, in mpg


(a) (6 points) Select the different manufacturers (makes) of the cars in this data set. Save this vector in a variable called `makes`

```{r}
makes <- select(vehicles, make)
makes
```



(b) (6 points) Can you determine how many different car manufacturers are represented by the data set? 128

```{r}
vehicles %>%
  group_by(make) %>%
  summarise(totals = n())
```
using unique

```{r}
unique(makes)
```




(c) (6 points) Filter the data set for vehicles manufactured in 1998.

```{r}
filter(vehicles, year == 1998)
```


(d) (8 points) Mutate the 1998 cars data frame to add a column `average` that has the average gas mileage (between city and highway MPG) for each car

```{r}
mutate(vehicles, average = (hwy + cty) / 2 )
```


(e) (8 points) Of all vehicles, what is the vehicle ID of the vehicle with the worst highway MPG? 1178

```{r}
vehicles %>%
  arrange(+hwy)
```


(f) (8 points) Which 2013 Acura model has the best highway MPG? Which 2015 Honda model has the best highway MPG?

```{r}
vehicles %>%
  filter(year == 2013, make == "Acura") %>%
  arrange(-hwy)
```
```{r}
vehicles %>%
  filter(year == 2015, make == "Honda") %>%
  arrange(-hwy)
```

```{r}
vehicles %>%
  filter(year == 2013, make == "Acura") %>%
  
```


# Problem 2

Load the `nycflights13` packages. 

```{r}
library(nycflights13)
```

```{r}
flights
```


Use the `flights` dataframe to answer the following questions. 

(a) (6 points) Find all flights headed to TPA, and select only the origin, destination, and the departure time.

```{r}
flights %>%
  filter(dest == "TPA") %>%
  select(origin, dest, dep_time)
```


(b) (6 points) Consider flights from JFK to MCO. What was the average, minimum, and maximum _air time_
of those flights? 

```{r}
flights %>%
  filter(origin == "JFK", dest == "MCO") %>%
  summarise(average = mean(air_time, na.rm = TRUE), minimum = min(air_time, na.rm = TRUE), maximum = max(air_time, na.rm = TRUE))
```

(c) (6 points) What was the average _departure delay_ in each month? Save this as a data frame `dep_delay_by_month`. (Hint: you may have to perform a grouping operation then summarizing your data).

```{r}
dep_delay_by_month <- flights %>%
  group_by(month) %>%
  summarise(avg_dep_delay = mean(dep_delay, na.rm = TRUE))
dep_delay_by_month
```


(d) (8 points) Which month had the greatest average _departure delay_?

```{r}
max(dep_delay_by_month$avg_dep_delay)
```


(e) (8 points) To which destinations were the average _arrival delays_ the highest?

```{r}
flights %>%
  group_by(dest) %>%
  summarise(avg_arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(desc(avg_arr_delay))
```


(f) (8 points) Which airline had the smallest average _arrival delay_?

```{r}
flights %>%
  group_by(dest) %>%
  summarise(avg_arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(avg_arr_delay)
```


(g) (8 points) Find all flights that were operated by United, American, or Delta.

```{r}
flights %>%
  filter(carrier == "UA" | carrier == "AA" | carrier == "DL")
```


(h) (8 points) Find all the flights (if any) headed to Orlando (ORD), Tampa (TPA), or Miami (MIA) with a scheduled departure time later than 8:00 PM.

```{r}
flights %>%
  filter(dest == "ORD" | dest == "TPA" | dest == "MIA", sched_dep_time > 480)
```




