---
title: "Introduction to Data Science - HW 3"
author: "First Name Last name - `flastname@floridapoly.edu`"
output: html_notebook
---



# Problem 1 

(a) (10 points) Define a function `imperial_to_metric` that takes in **two arguments**: a number of feet and a number of inches. The function should return the equivalent length in meters

> To convert a length `L` from feet (`ft`) and inches (`inches`) to meters (`m`), one can use the relation: `L(m) = L(ft) × 0.3048 + L(inches) × 0.0254`

```{r}
imperial_to_metric <- function(ft, inches){
  return(ft * 0.3048 + inches * 0.0254)
}
imperial_to_metric(1, 12)
```


(b) (5 points) Create a variable `height_in_meters` by passing your height in imperial to the `imperial_to_metric` function.

```{r}
height_in_meters <- imperial_to_metric(6, 1)
height_in_meters
```



# Problem 2

`R` comes with many functions that you can use to do sophisticated tasks like random sampling. For example, you can round a number with the `round()` function, or calculate its factorial with the `factorial()` function. Using a function is pretty simple. Just write the name of the function and then the data you want the function to operate on in parentheses.

(a) (5 points) Find `round(3.1415)`, `factorial(12)`, `mean(1:17)`.

```{r}
round(3.1415)
factorial(12)
mean(1:17)
```


(b) (5 points) You can create an object named `die` that contains the numbers one through six:

```{r}
# Create a vector with numbers from 1 to 6
die <- 1:6
```

You can simulate a roll of the die with `R`’s `sample()` function. `sample()` takes two arguments: a vector named `x` and a number named `size`. 

Try `sample(x = die, size = 1)`. 

Is there any difference if you type `sample(die, size = 1)` ? Yes


```{r}
sample(x = die, size = 1)
sample(die, size = 1)
```



# Problem 3

Use `R` as a calculator to compute the following values:

(a) (5 points) $27 (38 -17)$

(b) (5 points) $ln(14^7)$

(c) (5 points) $\sqrt\frac{436}{12}$  FINISH


```{r}
27 * (38 - 17)
log((14^7))
sqrt(436/12)
```
FINISH


# Problem 4

Create the following vectors in `R`:

$a = (5, 10, 15, 20, ..., 160)$

$b = (87, 86, 85, ..., 56)$

```{r}
a <- seq(5, 160, by = 5)
b <- seq(87, 56, by = -1)
```

(a) (5 points) Multiply these vectors and call the result `d`. 

```{r}
d <- a * b
```


(b) (15 points) Select subsets of `d` to identify the following.

- What are the 19th, 20th, and 21st elements of `d`?

- What are all of the elements of `d` which are less than 2000?

- How many elements of `d` are greater than 6000?

```{r}
d[19:21]
d[d < 2000]
d[d > 6000]
```


# Problem 5

Start with this vector of `nouns`.  

```{r}
nouns <- c("apple", "flower", "insect", "lettuce", "knife", "dog", "cloud", "person", "cabinet", "flower" )
```

(a) (5 points) Use the `length()` function to display the number of elements in `nouns`.

```{r}
length(nouns)
```


(b) (5 points) Use indexing to create a new vector consisting of the first 4 elements of `nouns`.

```{r}
nouns[1:4]
```


(c) (5 points) Use indexing to create a new vector consisting of only the last 8 elements of `nouns`.

```{r}
nouns_last_eight <- nouns[3:8]
nouns_last_eight
```


(d) (5 points) Use indexing to create a new vector of the 1st, 3rd through 6th, and 10th elements of `nouns` (the length of the resulting vector should be 6)

```{r}
nouns_irregular <- nouns[c(1, 3, 6, 10)]
nouns_irregular
length(nouns_irregular)
```


(e) (5 points) Create a new vector with the elements of `nouns` in reverse order.

```{r}
nouns_reverse <- nouns[10:1]
nouns_reverse
```


# Problem 6

Consider the function `rescale01` defined as 

```{r}
rescale01 <- function(x) {
  rng <- range(x, na.rm = TRUE, finite = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
}
```

(a) (5 points) Evaluate `rescale01(c(0, 5, 10))`

```{r}
rescale01(c(0, 5, 10))
```

(b) (5 points) Describe what the `rescale01` function does.

The rescale01 function rescales the range to be between the values 0 and 1.

(c) (5 points) What would happen if `x` contained a single missing value, and `na.rm` was `FALSE`? Show an example.

```{r}
rescale01 <- function(x) {
  rng <- range(x, na.rm = FALSE, finite = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
}
rescale01(c(1, NA, 3))
```
The NA values are returned

> Hint: check the documentation (help page) for `range()`.




